Most existing online handwriting recognition techniques depend on a pen up/pen down gesture to window the input data. Essentially, there is a known beginning and end to user input. This paper does not make this assumption. We are using an input device that constantly streams the location of the fingers within its field of view so the pen up/down gesture is not as easily identified. \\[1\baselineskip]
One technique used in the process is the segmentation of the data points. This is difficult as it is hard to determine the beginning and end of segments, so typically unsupervised learning and data-driven approaches are used~\cite{plamondon2000online}. The statistical approaches to this problem use Hidden Markov Models or use a combination of HMMs and neural networks to recognize characters~\cite{plotz2009markov}. Hilbert Warping has been proposed as an alignment method for handwriting recognition~\cite{ishida2010hilbert}. Other scenarios have been proposed, including one where an LED pen is tracked in the air. This allows for 3D data to be interpreted, but also makes sure that the beginning and end of input are clearly defined~\cite{asano2010visual}. Finally, treating the handwriting problem like speech recognition, ie treating the input points as a signal, allows in place algorithms with handwriting feature vectors to be used, but the same problem of segmentation arises~\cite{starner1994online}. These techniques have problems with accuracy in identification. \\[1\baselineskip]
Another area of application of these techniques is sketch recognition, or digitizing drawings. The methods typically involve searching for sketch primitives and then combining them, which also rely on pen up/pen down gestures~\cite{hammond2011recognizing}. 
